::: {.content-hidden unless-format="html"}
$$
\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
$$
:::


# Exercises I

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "areal", "spdep", "spatialreg", "tmap", "viridisLite",
          "ggplot2", "ggthemes", "gridExtra") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```

### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```



## General Exercises

### 1) Can you import the spatial administrative units of Germany ("Kreisgrenzen_2020_mit_Einwohnerzahl" from the _data folder) and make a simple map of the geographies / adminstrative boundaries?   {.unnumbered}


### 2) What is the Coordinate reference system of this German shape file? Please print the CRS. {.unnumbered}



### 3) Using the MSOA data in London from above: Please draw a map showing the distribution of the share of non-EU immigrants (the variable is `per_nonEU').  {.unnumbered}


### 4) Below we will load some additional data on heat islands.   {.unnumbered}

We will add some Data about [London's Urban Heat Island](https://data.london.gov.uk/dataset/london-s-urban-heat-island---average-summer/). It contains information about the mean temperature at midnight during the summer of 2011.

This is a tif file that we need to read in with stars and then transform into sf.


a) On which projection is the urbclim temperature data?

b) Can you please calculate the average night-time temperature for each MSOA using area weighted interpolation. Make sure that the objects are on the same projections / crs.

c) Create a map showing the temperature for each MSOA, and plot it next to the maps of non-EU immigrant residents (e.g. using `grid.arrange()`) .





### 4) What's the correlation between the share of non-EU residents and the temperature.   {.unnumbered}



