::: {.content-hidden unless-format="html"}
$$
\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
$$
:::


# Exercises Ib

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "areal", "spdep", "spatialreg", "tmap", "viridisLite",
          "ggplot2", "ggthemes", "gridExtra") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```

### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```





## General Exercises


### 6) Please use the msoa.spdf and calculate a neighbours weights matrix of the nearest 10 neighbours (see `spdep::knearneigh()`), and create a listw object using row normalization. {.unnumbered}



### 7) OPTIONAL: Can you create a map containing the MSOA unit "City of London" (this is the most central MSOA around Tower Bridge, its code is MSOA11CD = "E02000001"). Can you also identify its ten nearest neighbours (the ten MSOA surrounding MSOA11CD = "E02000001") and also plot them all together? {.unnumbered}




### 8) Please calculate the queens neighbours and make a listw object that includes the second order neighbours (the neighbours of the neighbours). See the function `nblag()`. {.unnumbered}



### 9) Please calculate the inverse distance weighted neighbours with a 5km cutoff point (create the listw object using `nb2listwdist()` and minmax normalisation.   {.unnumbered}




### 10) Chose any characteristic from the data (e.g. ethnic groups or house prices) and calculate global Moran's I for it.   {.unnumbered}




### 11)  Produce a LISA cluster map for the characteristic you have chosen.   {.unnumbered}




### 12) Transform the queens neighbours listw object into a matrix format. {.unnumbered}



### 13) What do you get when you multiply a variable (data column) such as the home owner rate with your weights matrix? {.unnumbered}




