::: {.content-hidden unless-format="html"}
$$
\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
$$
:::


# Exercises I

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "tmap", "viridisLite",
          "ggplot2", "ggthemes") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```

### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```



## General Exercises

### 1) Can you import the spatial administrative units of Germany ("Kreisgrenzen_2020_mit_Einwohnerzahl" in _data folder) and make a simple plot of the boundaries? {.unnumbered} 



### 2) What is the Coordinate reference system of this German shape file? {.unnumbered}




### 3) Please use the msoa.spdf and calculate a neighbours weights matrix of the nearest 10 neighbours (see `spdep::knearneigh()`), and create a listw object using row normalization. {.unnumbered}



### 4) OPTIONAL: Can you create a map containing the City of London (MSOA11CD = "E02000001") and its ten nearest neighbours? {.unnumbered}




### 5) Please use the msoa.spdf and calculate a neighbours weights matrix of the nearest 10 neighbours (see `spdep::knearneigh()`), and create a listw object using row normalization. {.unnumbered}




### 6) Please calculate the queens neighbours and make a listw object that includes the second order neighbours (see `nblag()`). {.unnumbered}



### 7) Generate a matrix from the listw object {.unnumbered}



### 8) What do you get when you multiply a variable (data column) such as the home owner rate with your weights matrix? {.unnumbered}


