\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}

# Exercises II

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "tmap", "viridisLite") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```

### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```


## Environmental inequality

How would you investigate the following descriptive research question: Are immigrant minorities in London exposed to higher levels of pollution? Also consider the spatial structure. What's your dependent and what is your independent variable?

### 1) Define a neigbours weights object of your choice {.unnumbered}

Assume a typical neighbourhood would be 2.5km in diameter

```{r}
coords <- st_centroid(msoa.spdf)

# Neighbours within 3km distance
dist_15.nb <- dnearneigh(coords, d1 = 0, d2 = 2500)

summary(dist_15.nb)

# There are some empty neighbour sets. Lets impute those with the nearest neighbour.
k2.nb <- knearneigh(coords, k = 1)

# Replace zero
nolink_ids <- which(card(dist_15.nb) == 0)
dist_15.nb[card(dist_15.nb) == 0] <- k2.nb$nn[nolink_ids, ]

summary(dist_15.nb)

# listw object with row-normalization
dist_15.lw <- nb2listw(dist_15.nb, style = "W")
```


### 2) Estimate the extent of spatial auto-correlation in air pollution {.unnumbered}

```{r}
moran.test(msoa.spdf$no2, listw = dist_15.lw)
```


### 3) Estimate a Spatial SAR regression model {.unnumbered}

```{r}
mod_1.sar <- lagsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = FALSE) # we could here extend to SDM
summary(mod_1.sar)
```


### 4) Estimate a Spatial SEM regression model {.unnumbered}

```{r}
mod_1.sem <- errorsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = FALSE) # we could here extend to SDEM
summary(mod_1.sem)
```



### 5) Estimate a Spatial SLX regression model {.unnumbered}

```{r}
mod_1.slx <- lmSLX(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw)
summary(mod_1.slx)
```



### 6) Estimate a Spatial Durbin regression model {.unnumbered}

```{r}
mod_1.dub <- lagsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = TRUE) # Extend here to Durbin
summary(mod_1.dub)
```

### 7) Estimate a Spatial Durbin Error regression model {.unnumbered}

```{r}
mod_1.dube <- errorsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = TRUE) # Extend here to Durbin
summary(mod_1.dube)
```

### 8) Sneak preview on tomorrow: Which of the spatial model specifications about would you choose / prefer in a real world example?

### 9) Please calculate the spatially lagged value of the median house price.

```{r}
# Use lag.listw to lag variable
splag <- lag.listw(dist_15.lw,
                   var = msoa.spdf$med_house_price)

msoa.spdf$w.med_house_price <- splag

# Compare
summary(msoa.spdf$med_house_price)
summary(msoa.spdf$w.med_house_price)
```

### 10) Can you use the results of the previous task to run a non-linear SLX model, where you predict if an MSOA is within the ulez zone based on the house prices? Can you make sense of the result?

```{r}
### Calculate SLX logit
mod_2.log <- glm(ulez ~ med_house_price + w.med_house_price,
                 data = msoa.spdf,
                 family = "binomial")
summary(mod_2.log)
```


```{r}
### Distance to city center
# Define centre
centre <- st_as_sf(data.frame(lon = -0.128120855701165, 
                              lat = 51.50725909644806),
                   coords = c("lon", "lat"), 
                   crs = 4326)
# Reproject
centre <- st_transform(centre, crs = st_crs(msoa.spdf))
# Calculate distance
msoa.spdf$dist_centre <- as.numeric(st_distance(msoa.spdf, centre)) / 1000
# hist(msoa.spdf$dist_centre)

### Add distance to city centre
mod_2.log <- glm(ulez ~ med_house_price + w.med_house_price + dist_centre,
                 data = msoa.spdf,
                 family = "binomial")
summary(mod_2.log)
```

