::: {.content-hidden unless-format="html"}
$$
\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
$$
:::

# Exercises II

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "tmap", "viridisLite") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```

### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```


## Environmental inequality

We would like to investigate the following descriptive research question: Are immigrant minorities in London exposed to higher levels of pollution? One could for instance do the following: use pollution as the outcome, and test if demographics (e.g. the share of immigrant minorities) predicts the level of pollution. We also want to consider the spatial structure: is it only the focal unit that matters or spatial clusters with high shares of minorities?

### 1) Define a neigbours weights object of your choice {.unnumbered}

Let's assume a typical neighbourhood would be 2.5km in diameter, so we can use distance based neighbours.



### 2) Estimate the extent of spatial auto-correlation in air pollution {.unnumbered}



### 3) Estimate a Spatial SAR regression model {.unnumbered}


### 4) Estimate a Spatial SEM regression model {.unnumbered}



### 5) Estimate a Spatial SLX regression model {.unnumbered}



### 6) Estimate a Spatial Durbin regression model {.unnumbered}


### 7) Estimate a Spatial Durbin Error regression model {.unnumbered}


### 8) Sneak preview on tomorrow: Which of the spatial model specifications about would you choose / prefer in a real world example?   {.unnumbered}

### 9) Please calculate the spatially lagged value of the median house price.   {.unnumbered}


### 10) Can you use the results of the previous task to run a non-linear SLX model, where you predict if an MSOA is within the ulez zone based on the house prices? Can you make sense of the result?   {.unnumbered}


