::: {.content-hidden unless-format="html"}
$$
\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
$$
:::

# Exercises II

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "tmap", "viridisLite") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```

### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```


## Environmental inequality

We would like to investigate the following descriptive research question: Are immigrant minorities in London exposed to higher levels of pollution? One could for instance do the following: use pollution as the outcome, and test if demographics (e.g. the share of immigrant minorities) predicts the level of pollution. We also want to consider the spatial structure: is it only the focal unit that matters or spatial clusters with high shares of minorities?

### 1) Define a neigbours weights object the includes everything within a given distance as neighbours. {.unnumbered}

Let's assume a typical neighbourhood would be 2.5km in diameter, so we can use distance based neighbours.

```{r}
coords <- st_centroid(msoa.spdf)

# Neighbours within 3km distance
dist_15.nb <- dnearneigh(coords, d1 = 0, d2 = 2500)

summary(dist_15.nb)

# There are some empty neighbour sets. Lets impute those with the nearest neighbour.
k2.nb <- knearneigh(coords, k = 1)

# Replace zero
nolink_ids <- which(card(dist_15.nb) == 0)
dist_15.nb[card(dist_15.nb) == 0] <- k2.nb$nn[nolink_ids, ]

summary(dist_15.nb)

# listw object with row-normalization
dist_15.lw <- nb2listw(dist_15.nb, style = "W")
```


### 2) Estimate the level of spatial auto-correlation in air pollution using the spatial weights matrix you have created above. {.unnumbered}

```{r}
moran.test(msoa.spdf$no2, listw = dist_15.lw)
```


### 3) Estimate a Spatial SAR regression model to test the link between the share of ethnic minorities and air pollution. Usually that means that air pollution is your dependent variable and several variables desribing the ethnic or socio-economic composition are used as covariates. Obviously you can also include controls such as population density.  {.unnumbered}

```{r}
mod_1.sar <- lagsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = FALSE) # we could here extend to SDM
summary(mod_1.sar)
```


### 4) Estimate a Spatial SEM regression model for the same model as above. {.unnumbered}

```{r}
mod_1.sem <- errorsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = FALSE) # we could here extend to SDEM
summary(mod_1.sem)
```



### 5) Estimate a Spatial SLX regression model for the same model as above. {.unnumbered}

```{r}
mod_1.slx <- lmSLX(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw)
summary(mod_1.slx)
```



### 6) Estimate a Spatial Durbin regression model for the same model as above. {.unnumbered}

```{r}
mod_1.dub <- lagsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = TRUE) # Extend here to Durbin
summary(mod_1.dub)
```

### 7) Estimate a Spatial Durbin Error regression model for the same model as above. {.unnumbered}

```{r}
mod_1.dube <- errorsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = TRUE) # Extend here to Durbin
summary(mod_1.dube)
```

### 8) Sneak preview on future session: Which of the spatial model specifications about would you choose / prefer in a real world example?   {.unnumbered}

### 9) If we model spatial dependence in statistical models, it is sometimes helpful to calculate spatial lags by hand. Please calculate the spatial lag value of the median house price. See `lag.listw()`. {.unnumbered}

```{r}
# Use lag.listw to lag variable
splag <- lag.listw(dist_15.lw,
                   var = msoa.spdf$med_house_price)

msoa.spdf$w.med_house_price <- splag

# Compare
summary(msoa.spdf$med_house_price)
summary(msoa.spdf$w.med_house_price)
```

### 10) Can you use the results of the previous task to run a non-linear SLX model, where you predict if an MSOA is within the ulez zone based on the house prices? Can you make sense of the result?   {.unnumbered}

```{r}
### Calculate SLX logit
mod_2.log <- glm(ulez ~ med_house_price + w.med_house_price,
                 data = msoa.spdf,
                 family = "binomial")
summary(mod_2.log)
```


```{r}
### Distance to city center
# Define centre
centre <- st_as_sf(data.frame(lon = -0.128120855701165, 
                              lat = 51.50725909644806),
                   coords = c("lon", "lat"), 
                   crs = 4326)
# Reproject
centre <- st_transform(centre, crs = st_crs(msoa.spdf))
# Calculate distance
msoa.spdf$dist_centre <- as.numeric(st_distance(msoa.spdf, centre)) / 1000
# hist(msoa.spdf$dist_centre)

### Add distance to city centre
mod_2.log <- glm(ulez ~ med_house_price + w.med_house_price + dist_centre,
                 data = msoa.spdf,
                 family = "binomial")
summary(mod_2.log)
```

