\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}

# Exercise I

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "tmap", "viridisLite") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```

### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```


## Environmental inequality

How would you investigate the following descriptive research question: Are ethnic (and immigrant) minorities in London exposed to higher levels of pollution? Also consider the spatial structure. What's your dependent and whats your independent variable?

### 1) Define a neigbours weights object of your choice {.unnumbered}

Assume a typical neighbourhood would be 1.5km in diameter

```{r}
coords <- st_centroid(msoa.spdf)

# Neighbours within 3km distance
dist_15.nb <- dnearneigh(coords, d1 = 0, d2 = 2500)

summary(dist_15.nb)

# There are some mpty one. Lets impute with the nearest neighbour
k2.nb <- knearneigh(coords, k = 1)

# Replace zero
nolink_ids <- which(card(dist_15.nb) == 0)
dist_15.nb[card(dist_15.nb) == 0] <- k2.nb$nn[nolink_ids, ]

summary(dist_15.nb)

# listw object with row-normalization
dist_15.lw <- nb2listw(dist_15.nb, style = "W")

```


### 2) Estimate the extent of spatial auto-correlation {.unnumbered}

```{r}
moran.test(msoa.spdf$no2, listw = dist_15.lw)
```


### 3) Estimate a spatial SAR regression model {.unnumbered}

a) Estimate a spatial autoregressive SAR model

```{r}
mod_1.sar <- lagsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = FALSE) # we could here extend to SDM
summary(mod_1.sar)
```


b) Have a look into the true multiplier matrix $({\bm I_N}-\rho {\bm W})^{-1}\beta_k$

```{r}
W <- listw2mat(dist_15.lw)
I <- diag(dim(W)[1])

rho <- unname(mod_1.sar$rho)

M <- solve(I - rho*W)

M[1:10, 1:10]
```


c) Create an $N \times N$ effects matrix. What is the effect of unit 6 on unit 10?


```{r}
# For beta 1

beta <- mod_1.sar$coefficients

effM <- beta[2] * M

effM[1:10, 1:10]

# "Effect" of unit 6 on unit 10
effM[10, 6]
```


d) Calculate and interpret the summary impact measures.


```{r}
mod_1.sar.imp <- impacts(mod_1.sar, listw = dist_15.lw, R = 300)
summary(mod_1.sar.imp)
```


### 4) Is SAR the right model choice or would you rather estimate a different model? {.unnumbered}

e) How do results change once you specify a spatial Durbin model?


I am using a spatial Durbin error model here.


```{r}
mod_1.durb <- errorsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = TRUE)

summary(mod_1.durb)

mod_1.durb.imp <- impacts(mod_1.durb, listw = dist_15.lw, R = 300)
summary(mod_1.durb.imp, zstats = TRUE, short = TRUE)
```

