\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}

# Exercise I

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "tmap", "viridisLite") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```

### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```


## Environmental inequality

How would you investigate the following descriptive research question: Are ethnic (and immigrant) minorities in London exposed to higher levels of pollution? Also consider the spatial structure. What's your dependent and whats your independent variable?

### 1) Define a neigbours weights object of your choice {.unnumbered}

### 2) Estimate the extent of spatial auto-correlation {.unnumbered}

### 3) Estimate a spatial SAR regression model {.unnumbered}

a) Estimate a spatial autoregressive SAR model

b) Have a look into the true multiplier matrix $({\bm I_N}-\rho {\bm W})^{-1}\beta_k$

c) Create an $N \times N$ effects matrix. What is the effect of unit 6 on unit 10?

d) Calculate and interpret the summary impact measures.

### 4) Is SAR the right model choice or would you rather estimate a different model? {.unnumbered}



