::: {.content-hidden unless-format="html"}
$$
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\plim}{\operatornamewithlimits{plim}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Exp}{\mathrm{E}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\irow}[1]{%
\begin{pmatrix}#1\end{pmatrix}
}
$$
:::

# Exercises III

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "ggplot2", "tmap", "viridis", "viridisLite", 
          "plm", "lfe", "splm", "SDPDmod")
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```


### Reload data from pervious session {.unnumbered}

```{r}
load("_data/msoa2_spatial.RData")
```



## Environmental inequality (continued)

Let's use the same neighbours weights definition as before:

```{r}
coords <- st_centroid(msoa.spdf)

# Neighbours within 3km distance
dist_15.nb <- dnearneigh(coords, d1 = 0, d2 = 2500)

summary(dist_15.nb)

# There are some empty neighbour sets. Lets impute those with the nearest neighbour.
k2.nb <- knearneigh(coords, k = 1)

# Replace zero
nolink_ids <- which(card(dist_15.nb) == 0)
dist_15.nb[card(dist_15.nb) == 0] <- k2.nb$nn[nolink_ids, ]

summary(dist_15.nb)

# listw object with row-normalization
dist_15.lw <- nb2listw(dist_15.nb, style = "W")
```

and estiamte the spatial SAR model: 

```{r}
mod_1.sar <- lagsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU  + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = FALSE) # we could here extend to SDM
summary(mod_1.sar)
```


### 1) Please calculate the true multiplier matrix of this SAR model. {.unnumbered}

The multiplier matrix is given by $({\bm I_N}-\rho {\bm W})^{-1}$.

```{r}
W <- listw2mat(dist_15.lw)
I <- diag(dim(W)[1])

rho <- unname(mod_1.sar$rho)

M <- solve(I - rho*W)

M[1:10, 1:10]
```


### 2) Create an N x N effects matrix for the effect of the non-EU citizens. What is the effect of unit 6 on unit 10? Why is this larger than the effect of unit 5 on unit 8? {.unnumbered}


```{r}
# For beta 1

beta <- mod_1.sar$coefficients

effM <- beta["per_nonEU"] * M

effM[1:10, 1:10]

# "Effect" of unit 6 on unit 10
effM[10, 6]

# "Effect" of unit 5 on unit 8
effM[8, 5]
```


### 3) Calculate and interpret the summary impact measures of the SAR model. {.unnumbered}


```{r}
mod_1.sar.imp <- impacts(mod_1.sar, listw = dist_15.lw, R = 300)
summary(mod_1.sar.imp)
```


### 4) Is SAR the right model choice or would you rather estimate a different model? Please run a Durbin model and caculate its impact summary measures {.unnumbered}


```{r}
# Spatial Dubrbin model
mod_1.durb <- lagsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = TRUE)

summary(mod_1.durb)

# Impact measures of the Durbin Error model
mod_1.durb.imp <- impacts(mod_1.durb, listw = dist_15.lw, R = 300)
summary(mod_1.durb.imp, zstats = TRUE, short = TRUE)
```


### 5) Please repeat with a Durbin Error model. Why are the impacts here identical to the coefficients? {.unnumbered}

```{r}
# Spatial Dubrbin model
mod_1.durbe <- errorsarlm(log(no2) ~ per_mixed + per_asian + per_black + per_other
                      + per_nonUK_EU + per_nonEU + log(POPDEN),  
                      data = msoa.spdf, 
                      listw = dist_15.lw,
                      Durbin = TRUE)

summary(mod_1.durbe)

# Impact measures of the Durbin model
mod_1.durbe.imp <- impacts(mod_1.durbe, listw = dist_15.lw, R = 300)
summary(mod_1.durbe.imp, zstats = TRUE, short = TRUE)
```


