::: {.content-hidden unless-format="html"}
$$
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\plim}{\operatornamewithlimits{plim}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Exp}{\mathrm{E}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\irow}[1]{%
\begin{pmatrix}#1\end{pmatrix}
}
$$
:::

\newcommand{\Prob}{\mathrm{Prob}}

# Other Models

### Required packages

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "tmap", "viridisLite", "GWmodel") # note: load spdep first, then spatialreg
lapply(pkgs, require, character.only = TRUE)

```

### Session info

```{r}
sessionInfo()

```

### Reload data from pervious session

```{r}
load("_data/msoa2_spatial.RData")
```



## Geographically weighted regression

Does the relation between $y$ and $x$ vary depending on the region we are looking at? With geographically weighted regressions (GWR), we can exploit the spatial heterogeneity in relations / coefficients.

GWR [@Brunsdon.1996; @Gollini.2015] is mainly an explorative tool for spatial data analysis in which we estimate an equation at different geographical points. For $L$ given locations across London, we receive $L$ different coefficients.

$$
\begin{split} 
\hat{\bm \beta}_l=& ({\bm X}^\intercal{\bm M}_l{\bm X})^{-1}{\bm X}^\intercal{\bm M}_l{\bm Y},
\end{split}
$$

The $N \times N$ matrix ${\bm M}_l$ defines the weights at each local point $l$, assigning higher weights to closer units. The local weights are determined by a kernel density function with a pre-determined bandwidth $b$ around each point (either a fixed distance or an adaptive k nearest neighbours bandwidth). Models are estimated via `gwr.basic()` or `gwr.robust()` of the `GWmodel` package.

```{r}
# Search for the optimal bandwidth 
set.seed(123)
hv_1.bw <- bw.gwr(log(med_house_price) ~ log(no2) + log(POPDEN) + pubs_count ,
                  data = as_Spatial(msoa.spdf),
                  kernel = "boxcar",
                  adaptive = TRUE) 
hv_1.bw


### GWR 
hv_1.gwr <- gwr.robust(log(med_house_price) ~ log(no2) + log(POPDEN) + pubs_count,
                      data = as_Spatial(msoa.spdf), 
                      kernel = "boxcar", 
                      adaptive = TRUE, 
                      bw = hv_1.bw, 
                      longlat = FALSE)
print(hv_1.gwr)
```

The results give a range of coefficients for different locations. Let's map those individual coefficients.

```{r}
# Spatial object
gwr.spdf <- st_as_sf(hv_1.gwr$SDF)
gwr.spdf <- st_make_valid(gwr.spdf)

# Map
tmap_mode("view")

mp2 <- tm_shape(gwr.spdf) +
  tm_fill(col = "log(POPDEN)", 
          style = "cont", 
          # n = 8,
          title = "Coefficient", 
          palette = viridis(100),
          midpoint = TRUE, stretch.palette = TRUE) +
  tm_borders(col = "grey85") +
  tm_layout(legend.frame = TRUE, legend.bg.color = TRUE,
            #legend.position = c("right", "bottom"),
            legend.outside = TRUE,
            main.title = "Coefficient of log population density", 
            main.title.position = "center",
            title.snap.to.legend = TRUE) 

mp2 

```

Just from looking at the map, there may be a connection with the undergrpund network - the effect of population density on house values seems to be stronger / more positive where underground connection is weaker?!


## Non-Linear Models

Models with endogenous regressors (SAR)


- In the literature: mostly spatial probit considered

- Spatial logit rather uncommon (non normally distributed errors)


	
Issues with non-linear spatial models

- Estimation: with dependent observations, we need to maximize one $n$-dimensional (log-)likelihood instead of a product of $n$ independent distributions

- Estimation challenging and computationally intense

- Hard to interpret due to non-linear effects in non-linear models

	
@Elhorst.2017a, @Franzese.2016

### Problem with non-linear models

Spatial-SAR-Probit
$$
		{\bm y^\star}=\rho{\bm W}{\bm y^\star}+{\bm X}{\bm \beta}+ {\bm \varepsilon} \\		
		y_i = \{1 \text{ if } y_i^\star > 0; 0 \text{ if } y_i^\star \leq 0 \} \nonumber
$$

or in reduced form:
	
$$
		{\bm y^\star}=(\bm I - \rho{\bm W})^{-1}{\bm X}{\bm \beta} + \bm u \text{, } \bm u = (\bm I - \rho{\bm W})^{-1}{\bm \varepsilon},\\
		\text{with } \bm u \sim MVN(0, (\bm I - \rho{\bm W})^\intercal (\bm I - \rho{\bm W})^{-1}) \nonumber
$$

- Probability $\bm y^\star$ is a latent variable, not observed

- We only observe binary outcome $y_i$

- $\Cov(y_i, y_j)$ is not the same as $\Cov(y_i^\star, y_j^\star)$

- Error term is heteroskedastic and spatially correlated


Probability

$$
		\Prob[{\bm y^\star}>0]  = 
		\Prob[(\bm I - \rho{\bm W})^{-1}{\bm X}{\bm \beta} + 
		(\bm I - \rho{\bm W})^{-1}{\bm \varepsilon}] \\
		  =  \Prob[(\bm I - \rho{\bm W})^{-1}{\bm \varepsilon} <
		 (\bm I - \rho{\bm W})^{-1}{\bm X}{\bm \beta}] \nonumber
$$

	or in using the observed outcome:
	
$$
		\Prob[\bm y_i=1 | \bm X]  = 
		\Prob\big[u_i <
		 [(\bm I - \rho{\bm W})^{-1}{\bm X}{\bm \beta}]_i\big] \\
		  = \bm \phi\{[(\bm I - \rho{\bm W})^{-1}{\bm X}{\bm \beta}]_i 
		 / \sigma_{ui}\} 
$$
	
- $\bm \phi\{\}$ is an n-dimensional cumulative-normal distribution 

- $\sigma_{ui}$ equals $(\bm I - \rho{\bm W})^\intercal (\bm I - \rho{\bm W})^{-1})_{ii}$, not constant

- no analytical solution

### Estimation

Estimation methods for Spatial-SAR Probit / Logit

- Expectation Maximization [@McMillen.1992].

- (Linearized) Generalized Methods of Moments [@Klier.2008].

- Recursive Importance Sampling [@Beron.2004].

- Maximum Simulated Likelihood RIS [@Franzese.2016]

- Bayesian approach with Markov Chain Monte Carlo simulations [@LeSage.2009]: R package `spatialprobit`
	
Note that it can be hard to interpret the results. As in the linear case, it is necessary to compute the impacts. However, the `marginal' effects may vary with values of the independent variables and the location [@Lacombe.2018].

### Suggestion

	In case you are not familiar with the econometric estimation methods and spatial regression models, don't use non-linear models with AR term. 
	
	If necessary, I would recommend using `spatialprobit` relying on Bayesian MCMC (set high ndraw and burn-in, e.g. 7500 and 2500).


- So far, no `best practice' guide

- No systematic comparison of estimation methods

- In R: Only `spatialprobit` provides impact measures?

- Hard to interpret results

Work-around: If the specification is theoretical plausible, using SLX probit / logit might be a practical solution! 


