\newcommand{\Exp}{\mathrm{E}}
\newcommand\given[1][]{\:#1\vert\:}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\bm}[1]{\boldsymbol{\mathbf{#1}}}

# Exercise II

### Required packages {.unnumbered}

```{r, message = FALSE, warning = FALSE, results = 'hide'}
pkgs <- c("sf", "mapview", "spdep", "spatialreg", "tmap", "viridisLite", 
          "plm", "splm", "SDPDmod")
lapply(pkgs, require, character.only = TRUE)

```

### Session info {.unnumbered}

```{r}
sessionInfo()

```




## Inkar data

Below, we read and transform some characteristics of the [INKAR data](https://www.inkar.de/) on German counties.

```{r}
di <- c("_data/")

# Define the downloaded filed
j <- c("inkar.csv")
c <- 1

for(k in j){
  header <- as.vector(t(read.table(paste0(di, k), nrows = 1, sep = ";")[1,]))
  # Clean header
  header <- stringi::stri_replace_all_fixed(
    header, 
    c("ä", "ö", "ü", "Ä", "Ö", "Ü"), 
    c("ae", "oe", "ue", "Ae", "Oe", "Ue"), 
    vectorize_all = FALSE
  )
  header <- gsub(" ", "", header)
  header <- gsub("\\.", "", header)
  header <- iconv(header, "latin1", "ASCII", sub = "")
  
  # Combine with second row header (year)
  header2 <- as.vector(t(read.table(paste0(di, k), skip = 1, nrows = 1, sep = ";")[1,]))
  header3 <- paste(header, header2, sep = "_")
  header3 <- gsub("_NA", "", header3)
  
  nc <- length(header3)
  # Input and rename data
  data <- read.csv(paste0(di, k), skip = 2, header = FALSE, sep = ";", 
                   quote = "\"", dec = ",", stringsAsFactors = F,
                   colClasses = "character")
  names(data) <- header3
  data1 <- data
  
  # Correct character vars (containing thousands separator)
  vars <- which(sapply(data1, is.character))
  vars <- vars[-which(vars %in% c(1:3))]
  for(l in vars){
    data1[,l] <- gsub("\\.", "", data1[,l])
    data1[,l] <- gsub("\\,", ".", data1[,l])
    data1[,l] <- as.numeric(data1[,l])
  }
  
  
  # #Save
  # l <- paste("bearb", k, sep = "_")
  # write.table(data1, file = l, row.names = FALSE, sep = ";", dec = ".", na = ".")
  
  # #Reshape
  # helpvar1 <- unique(header[4:length(header)])
  # helpvar2 <-  sort(unique(header2[!is.na(header2)]))
  # n_vars <- length(helpvar1)
  # n_times <- length(helpvar2)
  # helpvar1 <- sort(rep(helpvar1, times = n_times))
  # helpvar2 <- rep(helpvar2, times = n_vars)
  # helpvar3 <- paste(helpvar1, helpvar2, sep = "_")
  # count <- ncol(data1)+1
  # for(v in helpvar3) {
  #   if(v %in% names(data1)) {}
  #   else{
  #     data1[,count] <- NA
  #     colnames(data1)[count] <- v
  #     count <- count+1
  #   }
  # }
  # data1 <- data1[c(colnames(data1)[1:3], sort(helpvar3))]
  # 
  # data1 <- reshape(data1, direction = "long", varying = 4:ncol(data1), 
  #                  sep = "_")
  data.long <- tidyr::pivot_longer(data1, 
                                  cols = 4:ncol(data1),
                                  names_to = c(".value", "year"),
                                  names_pattern = "(.*)_(.*)")
  
  
  colnames(data.long) <- substr(colnames(data.long), 1, 30)
  
  if(c == 1){
    inkar.df <- data.long
  }else{
    inkar.df <- merge(inkar.df, data.long, all.x = TRUE, all.y = TRUE)
  }
  
  c <- c+1
  
}



inkar.df$year <- as.numeric(inkar.df$year)

names(inkar.df)[which(names(inkar.df) == "Pkw-Dichte")] <- "pkw_dichte"

save(inkar.df, file = "_data/inkar.Rdata")

```


Variables are

| Variable | Description |
| ------------					   | ------------ |
| "Kennziffer"                      | ID                                         |
| "Raumeinheit"                     | Name                                       |
| "Aggregat"                        | Level                                      |
| "year"                            | Year                                       |
| "Bruttoinlandsproduktin1000Euro"  | Gross Domestic Product in 1000 euros       |
| "HaushaltemitKindern"             | Households with children                   |
| "Lebenserwartung"                 | Life expectancy                            |
| "KommunaleSchulden"               | Municipal debts                            |
| "Pkw-Dichte"                      | Car density                                |
| "Straenverkehrsunfaelle"          | Road traffic accidents                     |
| "Einpendler"                      | In-commuters                               |
| "Auspendler"                      | Out-commuters                              |
| "Beschaeftigtenquote"             | Employment rate                            |
| "Bevoelkerunggesamt"              | Population                                 |
| "Krankenhausbetten"               | Hospital beds per 1,000 inhabitants        |
| "Gesamtwanderungssaldo"           | Net migration balance                      |


## County shapes

```{r}
kreise.spdf <- st_read(dsn = "_data/Kreisgrenzen_2020_mit_Einwohnerzahl",
                       layer = "KRS_ew_20")
```

## Exercises

### Please map the life expectancy across Germany

### Test the effect of regional characteristics on life expectancy

1) Chose some variables that could predict life expectancy

2) __Chose between:__

a) Estimate a cross-sectional spatial model for a selected year

b) Estimate a spatial panel model (use the specification you prefer)

3) Calculate the impacts


### Esimate an FE model with SLX specification




<!-- We use the `WDI` API package to retrieve data from the World Bank. -->

<!-- You can open the [World Bank Data browser](https://databank.worldbank.org/home.aspx) to go though the data. -->

<!-- You can search for indicators with `WDIsearch()`. -->
<!-- ```{r warning=FALSE} -->
<!-- library(WDI) -->

<!-- # Search GDP per capita -->
<!-- WDIsearch("CO2 intensity") -->

<!-- # Political Stability -->
<!-- WDIsearch("Political Stability") -->

<!-- #  -->
<!-- WDIsearch("democracy") -->
<!-- # The Democracy indicator is an additive eleven-point scale (0-10) -->

<!-- ``` -->

<!-- ```{r, cache=TRUE} -->
<!-- # Define countries, indicators to query, and time period -->
<!-- wd.df <- WDI(country = "all",  -->
<!--              indicator = c('population' = "SP.POP.TOTL",  -->
<!--                            'gdp_pc' = "NY.GDP.PCAP.KD",  -->
<!--                            'co2_pc' = "EN.ATM.CO2E.PC", -->
<!--                            'co2_intesity' = "EN.ATM.CO2E.EG.ZS", -->
<!--                            'gini' = "SI.POV.GINI", -->
<!--                            'political_stability' = "GV.POLI.ST.ES", -->
<!--                            'inst_democr' = "UPP.INS.DEMO.XQ"), -->
<!--              extra = TRUE, -->
<!--              start = 2010, end = 2019) -->

<!-- # Save -->
<!-- save(wd.df, file = "_data/WDI_data.RData") -->
<!-- ``` -->


<!-- ## Diffusion of political regimes -->

<!-- See for instance @Gleditsch.2006 for an example for the diffusion of democratization. -->




